Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-03 WSSSPE3/report/WSSSPE3_review.tex
Acknowledgements: touched up.

Work by Katz was supported by the National Science Foundation while working at
the Foundation. Any opinion, finding, and conclusions or recommendations
expressed in this material are those of the author(s) and do not necessarily
reflect the views of the National Science Foundation. Choi's work is supported
in part by the National Science Foundation research grant DMS-1522687 and
a WSSSPE3 travel award. Hetherington was funded by
the Software Sustainability Institute, RCUK grants EP/H043160/1 and EP/N006410/1.
%
Work by Gunter was supported by the Office of Science, Office of Biological and
Environmental Research, of the US Department of Energy under Award Numbers
DE-AC02-05CH11231, DE-AC02-06CH11357, DE-AC05-00OR22725, and DE-AC02-98CH10886,
as part of the DOE Systems Biology Knowledgebase and by the Office of Science,
Office of Advanced Scientific Computing Research (ASCR) of the U.S. Department
of Energy under Contract Number DE-AC02-05CH11231 as part of the Template
Interfaces for Agile Parallel Data-Intensive Science (TIGRES) project.
%
\todo{feel free to add stuff here}

\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Organizing Committee}  \label{sec:orgcom}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\todo{Do we want email addresses here?}
The following is the list of organizers of WSSSPE3.

>>>>

Work by Katz was supported by the National Science Foundation while working at
the Foundation. Any opinion, finding, and conclusions or recommendations
expressed in this material are those of the author(s) and do not necessarily
reflect the views of the National Science Foundation.
%
Choi's work was supported in part by the National Science Foundation research
grant DMS-1522687 and a WSSSPE3 travel award. She thanks the encouragement and
discussion with Fred Hickernell.
%
Hetherington was funded by the Software Sustainability Institute, RCUK grants
EP/H043160/1 and EP/N006410/1.
%
Work by Gunter was supported by the Office of Science, Office of Biological and
Environmental Research, of the U.S.\ Department of Energy (DOE) under Award
Numbers DE-AC02-05CH11231, DE-AC02-06CH11357, DE-AC05-00OR22725, and
DE-AC02-98CH10886, as part of the DOE Systems Biology Knowledgebase and by the
Office of Science, Office of Advanced Scientific Computing Research (ASCR) of
the U.S.\ Department of Energy under Contract Number DE-AC02-05CH11231 as part
of the Template Interfaces for Agile Parallel Data-Intensive Science (TIGRES)
project.
%
%\todo{feel free to add stuff here}

\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Organizing Committee}  \label{sec:orgcom}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\todo{Do we want email addresses here?}

The following is the list of organizers of WSSSPE3.
